Draft - sGBJ

### 2024-12-19 reporting/master_draft/draft_sgbj.qmd
update report

@@

```{r descbreast}
##### Description
df_data |> 
  dplyr::select(age,
                event,
                time,
                grade) |> 
  gtsummary::tbl_summary()
```

@@

  facet_grid(grade ~ ., scales = "free_y") +
  scale_y_log10() +
  annotation_logticks(sides = "l") +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box="vertical") +
  labs(x = "SGBJ rank", y = "Raw p-value")
```

>>>>

load(here::here("data/breast_cancer/BreastCancer-Vijver-Clinical.RData"))

@@

```{r descbreast}
##### Description
df_data |> 
  dplyr::select(age,
                event,
                time,
                grade) |> 
  gtsummary::tbl_summary()

clin.data |> 
  mutate(event = factor(evmeta+evdeath>0,
                        levels = c(T,F),
                        labels = c("Yes", "No"))) |> 
  dplyr::select(Age = age,
                "Composite event" = event,
                "Follow-up" = tsurv,
                "Grade" = grade) |> 
    gtsummary::tbl_summary()

@@

  facet_grid(grade ~ ., scales = "free_y") +
  scale_y_log10() +
  annotation_logticks(sides = "l") +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box="vertical") +
  labs(x = "sGBJ rank", y = "Raw p-value")
```
